\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-10 Manuscript/Manuscript.tex
added figure and beginnings of results

\usepackage[]{lineno}
\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

\if0\blind
{
  \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
  \author{Zoe Macris}
\date{December 2023}
  \maketitle}

@@

Furthermore, according to \citet{Gtschi2015}, getting the appropriate amount of exercise has an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer . It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation \cite{Green2021}. \par
Beyond these individual benefits, cycling has a benefit for the environment and society as a whole. Transportation is a large source of greenhouse gas emissions for many countries \cite{Green2021}. In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas. Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation. It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions. Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.\par 
In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is  necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically.

@@

@@

The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{fig:Mateo-Babiano}

\begin{table}[tbp]
\small
\label{fig:Mateo-Babiano}
\centering
\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
\begin{tabular}{l*{5}{p{1.5cm}}}
\toprule
{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
\midrule
Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\usepackage[]{lineno}
\linenumbers*[1]

@@

\if0\blind
{
  \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
  \author{Zoe Macris\\
  University of Connecticut}
\date{December 2023}
  \maketitle}

@@

\subsection{Benefits of Cycling}
\label{sec:benefit}

According to \citet{Gtschi2015}, getting the appropriate amount of exercise has an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer . It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation \cite{Green2021}. \par
Beyond these individual benefits, cycling has a benefit for the environment and society as a whole. Transportation is a large source of greenhouse gas emissions for many countries \cite{Green2021}. In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas. Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation. It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions. Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit.\par 
In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it is necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically. Statistical analysis can come into play here and help prove whether bike lanes make a significant impact on the propensity of people cycling and their safety while doing it.

\subsection{Types of Infrastructure}
\label{sec:bikeshare}

The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.

@@

\section{Results}
\label{sec:results}

\subsection{Correlation and Regression Analysis}
\label{sec:corr}

2, 4, 5 Binary Probit Regression Analysis.

\subsection{Multiple Level Logistic Regression}
\label{sec:mult}

3. The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers. This analysis resulted in the data shown in Table ~\ref{fig:stress}.
\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
    \caption{Distribution of Stress by City from Teixeira Study}
    \label{fig:stress}
\end{figure}

\subsection{Generalized Linear Model}
\label{sec:gen}

@@

The paper by Mateo-Babiano takes the approach of using by Spearman correlation to analyse the effects of various cycling measures on usage, as can be seen in ~\ref{table:MB}

\begin{table}[tbp]
\small
\label{table:MB}
\centering
\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
\begin{tabular}{l*{5}{p{1.5cm}}}
\toprule
{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
\midrule
Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
\bottomrule
\end{tabular}
\end{table}
